---
title: "CoVPN COVID-19 Vaccine Efficacy Trial Immunogenicity Report"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
header-includes:
- \usepackage{fancyhdr}
- \usepackage{lipsum}
- \usepackage{caption}
- \fancyhead[LO,LE]{CoVPN COVID - 19 Vaccine Efficacy Trial Immunogenicity - Mock Report
                    Data as of `r format(Sys.Date(), '%B %d, %Y')`}
- \fancyfoot[LE,RO]{\thepage}
- \fancypagestyle{plain}{\pagestyle{fancy}}
output: 
  pdf_document
toc: true
classoption: 
  landscape
---

```{r knitr, echo = FALSE, message=FALSE, warning=F}
library(knitr)
library(kableExtra)
library(tidyverse)

base::load(here::here("data_clean", "params.Rdata"))
base::load(here::here("output","Tables.Rdata"))

# Determine output document type.
doctype <- opts_knit$get('rmarkdown.pandoc.to')
opts_chunk$set(echo = doctype == "html", message = doctype == "html")

```

\clearpage
\captionsetup[table]{labelformat=empty}

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Demographic", tbl_num)}`
```{r demo, results = "asis", eval = "demo" %in% names(tlf) & doctype != "docx"}

chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", trt_footer)

kable(tab_dm %>% select(-subgroup),
      col.names = c("Characteristics", sprintf("Placebo\n(N = %s)", sum(ds_s$Trt==0)), sprintf("Vaccine\n(N = %s)",sum(ds_s$Trt==1)), sprintf("Total\n(N = %s)", nrow(ds_s))),
      format = doctype, booktabs = TRUE, longtable = TRUE, caption=sprintf("Table %s. %s", tbl_num, title_i)) %>%
  pack_rows(index=table(tab_dm$subgroup)) %>%
  kable_styling(latex_options = "repeat_header") %>%
  footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)

tbl_num <- tbl_num + 1
```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Responder rates", tbl_num)}`
```{r respprop, results = "asis", eval = "respprop" %in% names(tlf) & doctype != "docx"}

chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab1 <- tab_rr %>% 
  select(subgroup, Group, Baseline, Visit,  N, Endpoint,Responder, `2-Fold Rise`, `4-Fold Rise`) %>% 
  mutate(N=as.character(N)) 

subnum <- 0
for (i in unique(tab_rr$subgroup)){
  subnum <- subnum + 1
  tab.i <- filter(tab1, subgroup==i) %>% 
    arrange(subgroup, Group, Baseline, Visit, Endpoint) %>%
    group_table(., c("Group", "Baseline", "Visit", "N", "Endpoint")) 
  
  print(kable(tab.i %>% select(-subgroup), 
              format = doctype, booktabs = TRUE, longtable = TRUE, 
              caption=sprintf("Table %s%s. %s by %s", tbl_num, letters[subnum], title_i, i)) %>%
          pack_rows(index=table(tab.i$subgroup)) %>%
          column_spec(1, width = "5cm") %>% 
          kable_styling(latex_options = "repeat_header") %>%
          footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)
  )
  
  cat("\n\n\\pagebreak\n")
}

tbl_num <- tbl_num + 1
```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Geometric mean titers (GMTs) or geometric mean value of concentrations (GMCs)", tbl_num)}`
```{r gmt, results = "asis", eval = "gmt" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab2 <- tab_gm %>% 
  select(subgroup, Group, Baseline, Visit, N, Endpoint, `GMT/GMC`, `95% CI`) %>% 
  mutate(N=as.character(N))

subnum <- 0
for (i in unique(tab2$subgroup)){ 
  subnum <- subnum + 1
  tab.i <- filter(tab2, subgroup==i) %>% 
  arrange(Group, Baseline, Visit, N, Endpoint) %>% 
  group_table(., c("Group", "Baseline", "Visit", "N", "Endpoint")) 
  
print(  
  kable(tab.i %>% select(-subgroup), 
        format = doctype, booktabs = TRUE, longtable = TRUE, 
        caption=sprintf("Table %s%s. %s by %s", tbl_num, letters[subnum], title_i, i)) %>%
  pack_rows(index=table(tab.i$subgroup)) %>%
     column_spec(1, width = "5cm") %>% 
  kable_styling(latex_options = "repeat_header") %>%
  footnote(general =  tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)
)
  cat("\n\n\\pagebreak\n")
}

tbl_num <- tbl_num + 1

```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. GMTRs or GMCRs between post-vaccinations vs. pre-vaccination", tbl_num)}`
```{r gmtr, results = "asis", eval = "gmtr" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab3 <- tab_gmr %>% 
  select(subgroup, Group, Baseline, Visit, N, Endpoint, `GMTR/GMCR`, `95% CI`) %>% 
  mutate(N=as.character(N)) 

subnum <- 0
for (i in unique(tab3$subgroup)){ 
  subnum <- subnum + 1
  tab.i <- filter(tab3, subgroup==i) %>% 
  arrange(Group, Baseline, Visit, N, Endpoint) %>% 
  group_table(., c("Group", "Baseline", "Visit", "N", "Endpoint")) 
  
  print(
    kable(tab.i %>% select(-subgroup), 
      format = doctype, booktabs = TRUE, longtable = TRUE, 
      caption=sprintf("Table %s%s. %s by %s", tbl_num, letters[subnum], title_i, i)) %>%
  kable_styling(latex_options = "repeat_header") %>%
  pack_rows(index=table(tab.i$subgroup)) %>%
  column_spec(1, width = "5cm") %>% 
  footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)
  )
  cat("\n\n\\pagebreak\n")
}

tbl_num <- tbl_num + 1

```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Ratios of GMTs/GMCs between the vaccine arm vs. placebo arm, by baseline status", tbl_num)}`
```{r RofGMTa, results = "asis", eval = "RofGMTa" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab4 <- tab_gmtrA %>%
  select(subgroup, Baseline, Visit, N, Endpoint, `Ratios of GMT/GMC`, `95% CI`) %>% 
  mutate(N=as.character(N)) %>% 
  arrange(subgroup, Baseline, Visit, N, Endpoint) %>% 
  group_table(., c("Baseline", "Visit", "N", "Endpoint")) %>% 
  ungroup()
  
  kable(tab4 %>% select(-subgroup), 
          format = doctype, booktabs = TRUE, longtable = TRUE, 
          caption=sprintf("Table %s. %s", tbl_num, title_i)) %>%
  kable_styling(latex_options = "repeat_header") %>%
  pack_rows(index=table(tab4$subgroup)) %>%
  footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)

tbl_num <- tbl_num + 1

```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Ratios of GMTs/GMCs between baseline positive participants vs. negative participants, among the vaccinees", tbl_num)}`
```{r RofGMTb, results = "asis", eval = "RofGMTb" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab5 <- tab_gmtrB %>% 
  select(subgroup, Visit, N, Endpoint, `Ratios of GMT/GMC`, `95% CI`) %>% 
  mutate(N=as.character(N)) %>% 
  arrange(Visit, N, Endpoint) %>% 
  group_table(., c("Visit", "N", "Endpoint")) %>% 
  ungroup()

kable(tab5 %>% select(-subgroup), 
      format = doctype, booktabs = TRUE, longtable = TRUE, #linesep=lineseps, 
      caption=sprintf("Table %s. %s", tbl_num, title_i)) %>%
  kable_styling(latex_options = "repeat_header") %>%
  pack_rows(index=table(tab5$subgroup)) %>%
  footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)

  tbl_num <- tbl_num + 1

```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Ratios of GMTs/GMCs between demographic subgroups among the vaccine recipients", tbl_num)}`
```{r RofGMTc, results = "asis", eval = "RofGMTc" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab6 <- tab_gmtrC %>% 
  ungroup() %>% 
  mutate(N=as.character(N), 
         subgroup=factor(comp_i, levels=c("Age", "Sex", "High Risk", "Ethnicity", "Minority"))) %>% 
  select(subgroup, Baseline, Visit, Endpoint, N, `Ratios of GMT/GMC`, `95% CI`) %>% 
  arrange(subgroup, Baseline, Visit, N, Endpoint) %>% 
  group_table(., c("Baseline", "Visit", "N", "Endpoint")) 


  kable(tab6 %>% select(-subgroup), 
        format = doctype, booktabs = TRUE, longtable = TRUE,
        caption=sprintf("Table %s. %s", tbl_num, title_i)) %>%
    kable_styling(latex_options = "repeat_header") %>%
    pack_rows(index=table(tab6$subgroup)) %>%
    footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)

tbl_num <- tbl_num + 1

```
\clearpage

`r if ("demo" %in% names(tlf)) {sprintf("### Table %s. Differences of responder rates between the vaccine arm and the placebo arm", tbl_num)}`
```{r respdiff, results = "asis", eval = "respdiff" %in% names(tlf) & doctype != "docx"}
chunk_name <- opts_current$get("label")
tlf_labels <- tlf[[chunk_name]]

title_i <- tlf_labels[["table_header"]]
footer_i <- tlf_labels[["table_footer"]]

tab_footer <- c(footer_i, "", add2footer, "", trt_footer)

tab7 <- tab_rrdiff %>% 
  select(subgroup, Group, Baseline, Visit, N, Endpoint, `2-Fold Rise`, `4-Fold Rise`, Responder) %>% 
  mutate(N=as.character(N)) %>% 
  ungroup()
  
subnum <- 0
for (i in unique(tab7$subgroup)){ 
  subnum <- subnum + 1

  tab.i <- filter(tab7, subgroup==i) %>% 
    arrange(subgroup, Group, Baseline, Visit, N, Endpoint) %>% 
    group_table(., c( "Group", "Baseline","Visit", "N", "Endpoint")) 
  
  print(
    kable(tab.i %>% select(-subgroup), 
          format = doctype, booktabs = TRUE, longtable = TRUE, 
          caption=sprintf("Table %s%s. %s by %s", tbl_num, letters[subnum], title_i, i)) %>%
      kable_styling(latex_options = "repeat_header") %>%
      column_spec(1, width = "5cm") %>% 
      footnote(general = tab_footer, general_title = " ", threeparttable = TRUE, escape = TRUE)
  )
  cat("\n\n\\pagebreak\n")
}
tbl_num <- tbl_num + 1

```
