---
title: Verification Report for Super Learner Risk Score Calculations
date: "`r format(Sys.time(), '%B %d, %Y')`"
header-includes:
    - \usepackage{xcolor}
output: pdf_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# obligatory to append to the top of each script #
library(here)
renv::activate(project = here::here("..", ".."))
source(here("..", "..", "_common.R"))
# tolerance level of tests
tol <- 1e-4
```

```{r, cv-auc-test}
# programmer
cvsl_rslt <- readRDS(here("..", "output", "cvsl_riskscore_cvaucs.rds"))
cvauc_table <- cvsl_rslt[[1]]$aucs
cvauc_sl <- cvauc_table[cvauc_table$Learner == "SL", c("AUC", "ci_ll", "ci_ul")]

# tester
cvsl_rslt_test <- readRDS(here("verification_code", "output", "cv_auc_tab.rds"))
cvauc_sl_test <- cvsl_rslt_test[,c("cvAUC", "ci.l", "ci.u")]
comp_table <- rbind(as.numeric(cvauc_sl), as.numeric(cvauc_sl_test))
pass_check1 <- all(abs(comp_table[1,] - comp_table[2,]) < tol)
```

```{r, risk-score-test}
# programmer
risk_score_frame <- readr::read_csv(here("..", "output", "vaccine_ptids_with_riskscores.csv"))
risk_scores <- risk_score_frame$risk_score

# tester
risk_scores_test <- readRDS(here("verification_code", "output", "risk_scores.rds"))

pass_check2 <- all(abs(risk_scores - risk_scores_test) < tol)
```

## Result

The verification `r ifelse(pass_check1 & pass_check2, "succeeded", "failed")`.

### CV-AUC of super learner

Figure 1.1 compares the CV-AUC of each prediction algorithm as well as the super learner and discrete super learner. The high risk result in this table is the CV-AUC of the super learner, which is the algorithm that the SAP specifies will be advanced to the analysis for the risk score. The other reported CV-AUCs in this table are deemed to be low risk, since their purpose in the analysis is merely descriptive. This test passes if the point estimate and confidence interval limits of the tester and programmers results are within `r tol`. Agreement within this level of tolerance was judged to have minimal impact on downstream analyses.

Below is the comparison of the programmer and tester's results for the point estimate and 95% confidence interval for CV-AUC.

```{r}
row.names(comp_table) <- c("Programmer", "Tester")
colnames(comp_table) <- c("CV-AUC", "95% CI", "95% CI")
knitr::kable(comp_table, digits = 6)
```

This test `r ifelse(pass_check1, "passed", "failed")`.

### Risk scores

The primary output of the baseline risk score analysis is the risk scores themselves. This test passes if the assigned risk scores for the vaccinated individuals as computed by the tester and programmer are all within `r tol` units of one another.

This test `r ifelse(pass_check2, "passed", "failed")`.


## Signatures

```{r echo = FALSE, message = FALSE, tidy = FALSE, cache = FALSE, results = 'asis'}
suppressWarnings({
suppressPackageStartupMessages({
library(knitr)
library(kableExtra)
library(tibble)
})})
options(kableExtra.latex.load_packages = FALSE, 
        knitr.table.format = "latex",
        knitr.kable.NA = '',
        width = 40,
        usethis.quiet = TRUE)
signature_table <- function(people){
  # check that the tables have correct variables
  if (!all(c("role", "name") %in% tolower(names(people)))) {
    stop(paste0("people table must have variables: role and name. ",
                "Contains: ", paste0(tolower(names(people)), collapse = ", ")))
  }
  
  people$signature <- NA
  people$date <- NA
  names(people) <- tolower(names(people))
  people[, c("role", "name", "signature", "date")] %>% 
  kable(col.names = c("Role", "Name", "Signature", "Date"),
        escape = FALSE, booktabs = FALSE) %>% 
    kable_styling(full_width = FALSE, position = "left") %>% 
    row_spec(0, background = rgb(184, 204, 228, maxColorValue = 255)) %>% 
    column_spec(1, width = "9em", border_left = TRUE) %>% 
    column_spec(2, width = "11em") %>% 
    column_spec(3, width = "15em") %>% 
    column_spec(4, width = "8em", border_right = TRUE)
}
tibble::tribble(
  ~ name,                ~ role,
  "Ellis Hughes",  "Tester"
) %>% 
  signature_table()
```