---
title: "Key statistics for the verification of CoR plots"
author: "Kendrick Li"
date: "4/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load the libraries and datasets

```{r load_lib_dat, warning = FALSE, message = FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(GGally)
library(scales)
library(tidyverse)
library(PResiduals)
source(here::here("..", "_common.R"))
source(here("code", "params.R"))
source(here("code", "covid_corr_plot_functions.R"))

dat.long.cor.subset <- readRDS(here(
  "data_clean",
  "long_cor_data.rds"
))
dat.cor.subset <- readRDS(here("data_clean", "cor_data.rds"))

```

## Plot 2.1; Boxplots of D57 Ab markers: baseline negative vaccine arms (boxplots_Day57_trt_vaccine_x_cc_BaselineNeg_mock.png)


*Minimum and maximum, quartiles, and mean or assay Day 57 readouts*

```{r verify_boxplots_D57}

label.cases <- c("PP Cases", "PP Non-cases", "Intercurrent Cases")

assay_case_mat1 <- expand.grid(assay = assays,
                              case = label.cases[1:2])



day57_sum_mat <- sapply(1:nrow(assay_case_mat1), function(aa) {

  subdat <- dat.long.cor.subset %>%
    filter(assay == as.character(assay_case_mat1$assay[aa]), Bserostatus == "Baseline Neg",
           Trt == "Vaccine", cohort_event == as.character(assay_case_mat1$case[aa])) %>%
    select(Day57) 
  
  return(summary(subdat$Day57))
}) %>% t %>% data.frame

day57_sum_df <- cbind(assay_case_mat1,
                      day57_sum_mat)
names(day57_sum_df) <- c("Assay", "Cohort Event", "Min", "1st. Qu.", "Median", "Mean", "3rd. Qu.", "Max")
print(day57_sum_df)
write_csv(day57_sum_df,
          here("verification", "boxplots_statistics_Day57_baselineNeg_vaccine.csv"))
```

## Plot 2.3; Boxplots of D29 Ab markers: baseline negative vaccine arm (boxplots_Day29_trt_vaccine_x_cc_BaselineNeg_mock.png)

*Minimum and maximum, quartiles, and mean or assay Day 29 readouts*

```{r verify_boxplots_D29}

label.cases <- c("PP Cases", "PP Non-cases", "Intercurrent Cases")

assay_case_mat2 <- expand.grid(assay = assays,
                              case = label.cases) %>% arrange(assay, case)



day29_sum_mat <- sapply(1:nrow(assay_case_mat2), function(aa) {

  subdat <- dat.long.cor.subset %>%
    filter(assay == as.character(assay_case_mat2$assay[aa]), Bserostatus == "Baseline Neg",
           Trt == "Vaccine", cohort_event == as.character(assay_case_mat2$case[aa])) %>%
    select(Day29) 
  
  return(summary(subdat$Day29))
}) %>% t %>% data.frame

day29_sum_df <- cbind(assay_case_mat2,
                      day29_sum_mat)
names(day29_sum_df) <- c("Assay", "Cohort Event", "Min", "1st. Qu.", "Median", "Mean", "3rd. Qu.", "Max")
print(day29_sum_df)
write_csv(day29_sum_df,
          here("verification", "boxplots_statistics_Day29_baselineNeg_vaccine.csv"))
```