---
title: 'Verification Report: Correlates of Risk Graphs'
author: "Di Lu"
date: "2021/07/26"
output: 
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(testthat)
library(here)
```

```{r helper-functions, include=FALSE}
quiet<-function(x,func,...){
  x2<-try(suppressWarnings(func(x,...)),silent = TRUE)
  if(inherits(x2,'try-error')){
    return(x)
  }else{
    return(x2)
  }
}
naturalize <- function(x, round_digits = NA){
  NAs <- sum(is.na(x)| x=="NaN")
  date_formats<-c("%Y/%m/%d","%Y-%m-%d","%d-%b-%Y")
  if(sum(is.na(quiet(x,as.numeric))) == NAs){
    x <- quiet(x,as.numeric)
    if(!is.na(round_digits)){
      x <- round(x,round_digits)
    }
    return(x)
  }else if(sum(is.na(quiet(x,as.Date,tryFormats = date_formats))) == NAs){
    return(quiet(x,as.Date,tryFormats = date_formats))
  }else{
    return(x)
  }
}
# Equal test to include NA comparisons as T/F
equal <- function(x1,x2, threshold){
  
  if (is.numeric(x1) & threshold != 0) {
    x1 <- abs(x1 - x2) <= (threshold * (abs(x1 + x2)/2))
    x2 <- rep(TRUE,length(x1))
  }
  
  c <- as.character(x1) == as.character(x2)
  c[ is.na(x1) | is.na(x2) ] <- (is.na(x1) == is.na(x2) )[ is.na(x1) | is.na(x2) ]
  c
  
}
compare_datasets <- function(cols,ds1,ds2,index, verbose = TRUE, round_digits = NA, thresholds = 0){
  res <- lapply(cols,function(column_name){
    
    if(is.list(round_digits)){
      if(column_name %in% names(round_digits)){
        round_digit <- round_digits[[column_name]]
      }else{
        round_digit <- round_digits[[".default"]]
      }
    }else{
      round_digit <- round_digits
    }
    
    if(is.list(thresholds)){
      if(column_name %in% names(thresholds)){
        threshold <- thresholds[[column_name]]
      }else{
        threshold <- thresholds[[".default"]]
      }
    }else{
      threshold <- thresholds
    }
    
    
    
    v1 <- naturalize( ds1[ order( ds1[[index]] ), column_name, drop = TRUE], round_digits = round_digit)
    v2 <- naturalize( ds2[ order( ds2[[index]] ), column_name, drop = TRUE], round_digits = round_digit)
    is_equal <- equal( v1, v2 , threshold = threshold)
    if ( !all( is_equal ) & verbose)
      print( paste0("`", column_name, "` is not equal. ", sum(!is_equal),"/", max(length(v1),length(v2)), " mismatches." ) )
    
    
    
    return( list(
      equal = all( is_equal ),
      diffs = data.frame(
        key = sort(ds1[[index]])[!is_equal],
        ds1 = v1[!is_equal],
        ds2 = v2[!is_equal],
        stringsAsFactors = FALSE
        ))
      )
  })
  
  names(res) <- cols
  
  resmatched <- do.call( 'c', lapply(res,`[[`,1))
  if( verbose ){
    message( "There are ", sum(!resmatched), " mismatched fields of ", length(resmatched),'.')
  }
  
  attr(res,"index") <- index
  
  class(res) <- "comparison"
  return( res )
}
print.comparison <- function(x,...){
  n_mismatch <- do.call('c',lapply(x,function(y){
    z <- nrow(y$diffs)
    if(z>0){
      z
    }else{
      NULL
    }
  }))
  
  for(comp in names(n_mismatch)){
      message( paste0("`", comp, "` is not equal. ", n_mismatch[[comp]], " mismatches." ) )
  }
}
rerun_failed_comparisons <- function( x, ds1, ds2){
  mismatched <- names(do.call('c',lapply(x,function(y){
    if(nrow(y$diffs)>0){
      1
    }else{
      NULL
    }
  })))
  compare_datasets(mismatched, ds1, ds2, index = attr(x,"index"))
}
reformat <- function(x, digits = 1){
  format(round(as.numeric(x),digits = digits), nsmall = digits)
}
```

## Description

This is the verification report for the `cor_graphical` folder of the `correlates_reporting` project for CoVPN. 

In the verification process, the outputs of `cor_graphical_verification_code.R` were visually compared against the plots listed in the file `cor_graphical/verification/verification_plan.pdf`. The values presented in the original plots were also generated independently by the tester and compared against the outputs generated by the original programmer.

The files `cor_graphical/verification/input/longer_cor_data_plot1.csv`, and \newline `cor_graphical/verification/input/plot.25sample1.csv`, 
 were provided by the original programmer to the tester for verification purposes.

## Data Verification

### Load `longer.cor.subset.plot1` 

```{r Load-Data1, message=FALSE}
dat.longer.cor.subset.plot1_verification <- read.csv(
  here("verification/output/dat.longer.cor.subset.plot1_verification.csv")
) %>% arrange(Ptid,assay,time)

original.longer.cor.subset.plot1<-read.csv(
  here("verification/input/longer_cor_data_plot1.csv")
) %>% arrange(Ptid,assay,time)

```

### Verification

```{r comparison1}
data_clean_comparison <- compare_datasets(
  cols =  colnames(dat.longer.cor.subset.plot1_verification), index = "Ptid",
  ds1 = dat.longer.cor.subset.plot1_verification, ds2 = original.longer.cor.subset.plot1
)

```
```{r echo=FALSE}

clean_comparison_pass <- all(sapply(data_clean_comparison, `[[`, "equal"))

```

`longer.cor.subset.plot1` generated by using `cor_graphical_verification_code.R` was `r ifelse(clean_comparison_pass, "equivalent to","different from")` the output generated by original programmer, and `r ifelse(clean_comparison_pass, "passes","fails")` verification.

### Load `plot.25sample1`

```{r Load-Data2, message=FALSE}
plot.25sample1_verification <- read.csv(
  here("verification/output/plot.25sample1_verification.csv")
) %>% arrange(Ptid,assay,time)

original.plot.25sample1<-read.csv(
  here("verification/input/plot.25sample1.csv")
) %>% arrange(Ptid,assay,time)

```

### Verification

```{r comparison2}
data_clean_comparison <- compare_datasets(
  cols =  colnames(plot.25sample1_verification), index = "Ptid",
  ds1 = plot.25sample1_verification, ds2 = original.plot.25sample1
)

```
```{r echo=FALSE}

clean_comparison_pass <- all(sapply(data_clean_comparison, `[[`, "equal"))

```

`plot.25sample1` generated by using `cor_graphical_verification_code.R` was `r ifelse(clean_comparison_pass, "equivalent to","different from")` the output generated by original programmer, and `r ifelse(clean_comparison_pass, "passes","fails")` verification.

### Verification of lineplot of Binding Antibody to Spike: baseline negative vaccine arm (2 timepoints)

```{r, include=FALSE}
boxplots_neg_vaccine_bindSpike_2_verification <- read.csv(
  here("verification/output/dat.longer.cor.subset.plot1_verification.csv")) %>%   
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)

original.boxplots_neg_vaccine_bindSpike_2<-read.csv(
  here("verification/input/longer_cor_data_plot1.csv")) %>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)

plot.25sample1<-read.csv(
  here("verification/input/plot.25sample1.csv")
)

lineplots_neg_vaccine_bindSpike_plot.25sample1_2_verification <- plot.25sample1_verification %>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 29","Day 57"))

original.lineplots_neg_vaccine_bindSpike_plot.25sample1_2 <- plot.25sample1 %>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 29","Day 57"))


```



```{r comparison3}
data_clean_comparison_boxplot <- compare_datasets(
  cols =  colnames(boxplots_neg_vaccine_bindSpike_2_verification), index = "Ptid",
  ds1 = boxplots_neg_vaccine_bindSpike_2_verification, 
  ds2 = original.boxplots_neg_vaccine_bindSpike_2
)

data_clean_comparison_lineplot <- compare_datasets(
  cols =  colnames(lineplots_neg_vaccine_bindSpike_plot.25sample1_2_verification), index = "Ptid",
  ds1 = lineplots_neg_vaccine_bindSpike_plot.25sample1_2_verification, 
  ds2 = original.lineplots_neg_vaccine_bindSpike_plot.25sample1_2
)


```
```{r echo=FALSE}

clean_comparison_pass_boxplot <- all(sapply(data_clean_comparison_boxplot, `[[`, "equal"))

clean_comparison_pass_lineplot <- all(sapply(data_clean_comparison_lineplot, `[[`, "equal"))

```

The violin plot, box plot and line plot generated by the tester were visually compared with the outputs generated by original programmer. 

Key statistics(min, 25th percentile, median, 75th percentile, max) shown in the box plot calculated by tester were `r ifelse(clean_comparison_pass_boxplot, "equivalent to","different from")` the numbers provided by original programmer, and `r ifelse(clean_comparison_pass_boxplot, "passes","fails")` verification.

Input data for the line plot generated by tester were `r ifelse(clean_comparison_pass_lineplot, "equivalent to","different from")` the data provided by original programmer, and `r ifelse(clean_comparison_pass_lineplot, "passes","fails")` verification.

### Verification of lineplot of Pseudovirus Neutralization ID50: baseline negative vaccine arm (2 timepoints)

```{r, include=FALSE}
boxplots_neg_vaccine_pseudoneutid50_2_verification <- read.csv(
  here("verification/output/dat.longer.cor.subset.plot1_verification.csv")) %>%   
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "pseudoneutid50",
         time %in% c("Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)

original.boxplots_neg_vaccine_pseudoneutid50_2<-read.csv(
  here("verification/input/longer_cor_data_plot1.csv")) %>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "pseudoneutid50",
         time %in% c("Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)

plot.25sample1<-read.csv(
  here("verification/input/plot.25sample1.csv")
)


lineplots_neg_vaccine_pseudoneutid50_plot.25sample1_2_verification <- plot.25sample1_verification%>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "pseudoneutid50",
         time %in% c("Day 29","Day 57"))


original.lineplots_neg_vaccine_pseudoneutid50_plot.25sample1_2 <- plot.25sample1%>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "pseudoneutid50",
         time %in% c("Day 29","Day 57"))


```

```{r comparison4}
data_clean_comparison_boxplot <- compare_datasets(
  cols =  colnames(boxplots_neg_vaccine_pseudoneutid50_2_verification), index = "Ptid",
  ds1 = boxplots_neg_vaccine_pseudoneutid50_2_verification, 
  ds2 = original.boxplots_neg_vaccine_pseudoneutid50_2
)

data_clean_comparison_lineplot <- compare_datasets(
  cols =  colnames(lineplots_neg_vaccine_pseudoneutid50_plot.25sample1_2_verification), index = "Ptid",
  ds1 = lineplots_neg_vaccine_pseudoneutid50_plot.25sample1_2_verification, 
  ds2 = original.lineplots_neg_vaccine_pseudoneutid50_plot.25sample1_2
)


```
```{r echo=FALSE}

clean_comparison_pass_boxplot <- all(sapply(data_clean_comparison_boxplot, `[[`, "equal"))

clean_comparison_pass_lineplot <- all(sapply(data_clean_comparison_lineplot, `[[`, "equal"))

```

The violin plot, box plot and line plot generated by the tester were visually compared with the outputs generated by original programmer. 

Key statistics(min, 25th percentile, median, 75th percentile, max) shown in the box plot calculated by tester were `r ifelse(clean_comparison_pass_boxplot, "equivalent to","different from")` the statistics provided by original programmer, and `r ifelse(clean_comparison_pass_boxplot, "passes","fails")` verification.

Input data for the line plot generated by tester were `r ifelse(clean_comparison_pass_lineplot, "equivalent to","different from")` the data provided by original programmer, and `r ifelse(clean_comparison_pass_lineplot, "passes","fails")` verification.

### Verification of lineplot of Binding Antibody to Spike: baseline negative vaccine arm (3 timepoints)

```{r, include=FALSE}
boxplots_neg_vaccine_bindSpike_3_verification <- read.csv(
  here("verification/output/dat.longer.cor.subset.plot1_verification.csv")) %>%   
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 1","Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)

original.boxplots_neg_vaccine_bindSpike_3<-read.csv(
  here("verification/input/longer_cor_data_plot1.csv")) %>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 1","Day 29","Day 57")) %>% 
  arrange(Ptid,assay,time)


lineplots_neg_vaccine_bindSpike_plot.25sample1_3_verification <- plot.25sample1_verification %>% 
    filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 1","Day 29","Day 57"))

original.lineplots_neg_vaccine_bindSpike_plot.25sample1_3 <- plot.25sample1%>%
  filter(Trt == "Vaccine", 
         Bserostatus == "Baseline Neg", 
         assay == "bindSpike",
         time %in% c("Day 1","Day 29","Day 57"))


```


```{r comparison5}
data_clean_comparison_boxplot <- compare_datasets(
  cols =  colnames(boxplots_neg_vaccine_bindSpike_3_verification), index = "Ptid",
  ds1 = boxplots_neg_vaccine_bindSpike_3_verification, 
  ds2 = original.boxplots_neg_vaccine_bindSpike_3
)

data_clean_comparison_lineplot <- compare_datasets(
  cols =  colnames(lineplots_neg_vaccine_bindSpike_plot.25sample1_3_verification), index = "Ptid",
  ds1 = lineplots_neg_vaccine_bindSpike_plot.25sample1_3_verification, 
  ds2 = original.lineplots_neg_vaccine_bindSpike_plot.25sample1_3
)


```
```{r echo=FALSE}

clean_comparison_pass_boxplot <- all(sapply(data_clean_comparison_boxplot, `[[`, "equal"))

clean_comparison_pass_lineplot <- all(sapply(data_clean_comparison_lineplot, `[[`, "equal"))

```


The violin plot, box plot and line plot generated by the tester were visually compared with the outputs generated by original programmer. 

Key statistics(min, 25th percentile, median, 75th percentile, max) shown in the box plot calculated by tester were `r ifelse(clean_comparison_pass_boxplot, "equivalent to","different from")` the statistics provided by original programmer, and `r ifelse(clean_comparison_pass_boxplot, "passes","fails")` verification.

Input data for the line plot generated by tester were `r ifelse(clean_comparison_pass_lineplot, "equivalent to","different from")` the data provided by original programmer, and `r ifelse(clean_comparison_pass_lineplot, "passes","fails")` verification.


## Signature
```{r echo = FALSE, message = FALSE, tidy = FALSE, cache = FALSE, results = 'asis'}
suppressWarnings({
suppressPackageStartupMessages({
library(knitr)
library(kableExtra)
library(tibble)
})})
options(kableExtra.latex.load_packages = FALSE, 
        knitr.table.format = "latex",
        knitr.kable.NA = '',
        width = 40,
        usethis.quiet = TRUE)
signature_table <- function(people){
  # check that the tables have correct variables
  if (!all(c("role", "name") %in% tolower(names(people)))) {
    stop(paste0("people table must have variables: role and name. ",
                "Contains: ", paste0(tolower(names(people)), collapse = ", ")))
  }
  
  people$signature <- NA
  people$date <- NA
  names(people) <- tolower(names(people))
  people[, c("role", "name", "signature", "date")] %>% 
  kable(col.names = c("Role", "Name", "Signature", "Date"),
        escape = FALSE, booktabs = FALSE) %>% 
    kable_styling(full_width = FALSE, position = "left") %>% 
    row_spec(0, background = rgb(184, 204, 228, maxColorValue = 255)) %>% 
    column_spec(1, width = "9em", border_left = TRUE) %>% 
    column_spec(2, width = "11em") %>% 
    column_spec(3, width = "15em") %>% 
    column_spec(4, width = "8em", border_right = TRUE)
}
tibble::tribble(
  ~ name,                ~ role,
  "Di Lu",  "Tester"
) %>% 
  signature_table()
```


