# Graphical Description of Immunogenicity Data {#immuno-graphical}

## Pairs plots of antibody markers for overall per-protocal cohort

### Baseline SARS-CoV-2 Negative

```{r immuno-graphical-setup, echo = FALSE, message = FALSE}
library(here)
library(latex2exp)
library(knitr)
here::i_am("immuno_graphical/report.Rmd")
```

```{r, fig.cap = "Pair plots of D29 Ab markers: baseline negative vaccine arm", eval = ('Day29' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Day29_Markers_BaselineNeg_vaccine_arm_",
    study_name, ".png"
  )
))
```


\clearpage
```{r, fig.cap = "Pair plots of D57 Ab markers: baseline negative vaccine arm", eval = ('Day57' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Day57_Markers_BaselineNeg_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D29 fold-rise over D1 Ab markers: baseline negative vaccine arm", eval = ('Delta29overB' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Delta29overB_Markers_BaselineNeg_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm", eval = ('Delta57overB' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Delta57overB_Markers_BaselineNeg_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 Binding Antibody to Spike: baseline negative vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'bindSpike' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_bindSpike_by_times_BaselineNeg_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 Binding Antibody to RBD: baseline negative vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'bindRBD' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_bindRBD_by_times_BaselineNeg_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 PsV Neutralization 50\\% Titer: baseline negative vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'pseudoneutid50' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_pseudoneutid50_by_times_BaselineNeg_vaccine_",
    study_name, ".png"
  )
))
```


\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 PsV Neutralization 80\\% Titer: Baseline negative vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'pseudoneutid80' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_pseudoneutid80_by_times_BaselineNeg_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 Positive

```{r, fig.cap = "Pair plots of D29 Ab markers: baseline positive vaccine arm", eval = ('Day29' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Day29_Markers_BaselinePos_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D57 Ab markers: baseline positive vaccine arm", eval = ('Day57' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Day57_Markers_BaselinePos_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm", eval = ('Delta29overB' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Delta29overB_Markers_BaselinePos_vaccine_arm_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm", eval = ('Delta57overB' %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_Delta57overB_Markers_BaselinePos_vaccine_arm_",
    study_name, ".png"
  )
))
```

```{r, fig.cap = "Pair plots of D1, D29 and D57 Binding Antibody to Spike: baseline positive vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'bindSpike' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_bindSpike_by_times_BaselinePos_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 Binding Antibody to RBD: baseline positive vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'bindRBD' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_bindRBD_by_times_BaselinePos_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 PsV Neutralization 50\\% Titer: baseline positive vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'pseudoneutid50' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_pseudoneutid50_by_times_BaselinePos_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Pair plots of D1, D29 and D57 PsV Neutralization 80\\% Titer: Baseline positive vaccine arm", eval = (all(c('B', 'Day29', 'Day57') %in% times) & 'pseudoneutid80' %in% assays)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "pairs_pseudoneutid80_by_times_BaselinePos_vaccine_",
    study_name, ".png"
  )
))
```

\clearpage
## RCDF plots of antibody markers for overall per-protocol cohort

```{r, fig.cap = "RCDF plots for D29 Ab markers: by baseline status x randomization arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_RCDF_Day29_trt_both_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: by baseline status x randomization arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_RCDF_Day57_trt_both_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: by baseline status x randomization arm", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_RCDF_Delta29overB_trt_both_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: by baseline status x randomization arm", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_RCDF_Delta57overB_trt_both_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: by baseline status for the vaccine arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: by baseline status for the vaccine arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 over D1 fold-rise Ab markers: by baseline status for the vaccine arm", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: by baseline status for the vaccine arm", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_bstatus_both_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_bstatus_Neg_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_bstatus_Neg_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_bstatus_Neg_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_bstatus_Neg_",
    study_name, ".png"
  )
))
```

\clearpage
## Scatter plots of antibody markers versus age for overall per-protocol cohort

### Baseline SARS-CoV-2 negative

```{r, fig.cap = "Scatter plots for D29 Ab markers vs. age: baseline negative vaccine arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "scatter_Day29_vs_age_trt_Vaccine_BaselineNeg_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Scatter plots for D57 Ab markers vs. age: baseline negative vaccine arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "scatter_Day57_vs_age_trt_Vaccine_BaselineNeg_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 positive

```{r, fig.cap = "Scatter plots for D29 Ab markers vs. age: baseline positive vaccine arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "scatter_Day29_vs_age_trt_Vaccine_BaselinePos_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Scatter plots for D57 Ab markers vs. age: baseline positive vaccine arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0(
    "scatter_Day57_vs_age_trt_Vaccine_BaselinePos_",
    study_name, ".png"
  )
))
```

\clearpage
## Box plots of antibody markers for overall per-protocol cohort

### Baseline SARS-CoV-2 negative

```{r, fig.cap = "Boxplots of D29 Ab markers: baseline negative vaccine + placebo arms", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day29_x_trt_BaselineNeg_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline negative vaccine + placebo arms", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day57_x_trt_BaselineNeg_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline negative vaccine + placebo arms", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta29overB_x_trt_BaselineNeg_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine + placebo arms", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta57overB_x_trt_BaselineNeg_", study_name, ".png")
))
```

\clearpage
### Baseline SARS-CoV-2 positive

```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine + placebo arms", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day29_x_trt_BaselinePos_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine + placebo arms", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day57_x_trt_BaselinePos_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine + placebo arms", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta29overB_x_trt_BaselinePos_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine + placebo arms", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta57overB_x_trt_BaselinePos_", study_name, ".png")
))
```

\clearpage
### Baseline negative vs. positive vaccine recipients

```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive + negative vaccine arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day29_x_bstatus_vaccine_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive + negative vaccine arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day57_x_bstatus_vaccine_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive + negative vaccine arm", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta29overB_x_bstatus_vaccine_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive + negative vaccine arm", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta57overB_x_bstatus_vaccine_arm_", study_name, ".png")
))
```

\clearpage
### Baseline negative vs. positive placebo recipients

```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive + negative placebo arm", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day29_x_bstatus_placebo_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive + negative placebo arm", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Day57_x_bstatus_placebo_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive + negative placebo arm", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta29overB_x_bstatus_placebo_arm_", study_name, ".png")
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive + negative placebo arm", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("boxplots_Delta57overB_x_bstatus_placebo_arm_", study_name, ".png")
))
```

\clearpage
## Spaghetti plots of antibody markers over time for the overall per-protocol cohort

### Baseline SARS-CoV-2 negative

```{r, fig.cap = "Spaghetti plots of Ab markers over time: baseline negative vaccine + placebo arm", eval = all(c("B", "Day29", "Day57") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("spaghetti_plot_BaselineNeg_", study_name, ".png")
))
```

\clearpage
### Baseline SARS-CoV-2 positive
```{r, fig.cap = "Spaghetti plots of Ab markers over time: baseline positive vaccine + placebo arm", eval = all(c("B", "Day29", "Day57") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("spaghetti_plot_BaselinePos_", study_name, ".png")
))
```

\clearpage
## RCDF plots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 negative

```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by age groups.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by age groups.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by age groups.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age groups.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by high-risk condition.",eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by high-risk condition.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by age and high-risk condition.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and high-risk condition.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by sex assigned at birth.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by sex assigned at birth.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by age and sex assigned at birth.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and sex assigned at birth.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by ethnicity.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by ethnicity.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by race.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by race.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by race.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by race.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 positive

```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by age groups.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by age groups.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age groups.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age groups.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by race.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by race.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by race.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by race.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day29_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta29overB_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
## Boxplots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 negative

```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by age group.", eval=FALSE, eval = ("Day29" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by age group.", eval=FALSE, eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by age and sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by age and sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by ethnicity.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by ethnicity.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by ethnicity.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by ethnicity.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by race.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by race.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by race.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by race.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: Baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselineNeg_trt_vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: Baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: Baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 positive

```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by age group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by age group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by ethnicity.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by ethnicity.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by race.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by race.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by race.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by race.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day29_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval=FALSE}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D29 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta29overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta29overB_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = "Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```
