---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Univariate CoR: Nonparametric Threshold Modeling {#cor-threshold}



An extension of the unadjusted nonparametric threshold-searching approach developed in @Donovan, the covariate-adjusted TMLE-based approach developed by van der Laan, Zhang, Gilbert (in progress) is used to estimate the so-called threshold-response function $E_X[ E[Y|S \geq s, X, A = 1]|A=1]$ for a range of thresholds $s$. Here, $X$ is a set of baseline characteristics, $A=1$ represents the vaccine group, $S$ is the biomarker/immune-response/correlate of interest, and $Y$ is the indicator of COVID disease before some time point $t_f$. Intuitively, the threshold-response at a given threshold is the expected probability of obtaining COVID disease if one experiences a marker/immune-response value above that threshold. The threshold-response function is estimated for each of the four Day 57 antibody markers, in each case adjusting for the baseline covariates  --> age, baseline risk score, high risk indicator, and underrepresented minority status.A parametric learner, selected via cross-validation, is used for the covariate adjustment. A number of plots and tables are reported:
\begin{enumerate}
  \item A plot and table with risk estimates and point-wise 95\% confidence intervals for the threshold-response at a grid of thresholds.
   \item A plot and table with risk estimates and simultaneous 95\% confidence bands for the threshold-response at a grid of thresholds.
   \item A plot and table with threshold estimates and simultaneous 95\% confidence bands for the inverse threshold-response at a grid of risk values.
\end{enumerate}

A histogram of the marker values is superimposed on the threshold-response plots and a dashed red line is added to mark the threshold value after which no more events are observed.

For the estimates and inference of the threshold of protection at each risk level (based on the inverse threshold-response function, item 3) to be correct, we assume monotonicity of the true function $s \mapsto E_X[ E[Y|S \geq s, X, A = 1]|A=1]$. If the threshold-response function estimate does not seem to have a monotonic trend then the inverse threshold-response estimates and inference should be interpreted with caution.





\newpage
```{r, include = F}
marker <- "Spike protein antibody"
key <- "bindSpike"
day <- 57
```

```{r, child=c('sub_report.Rmd')}


```

\newpage 
```{r, include = F}
marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 57
```

```{r, child=c('sub_report.Rmd')}


```

\newpage 

```{r, include = F}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 57
```

```{r, child=c('sub_report.Rmd')}


```

\newpage 


```{r, include = F}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 57
```

```{r, child=c('sub_report.Rmd')}


```