---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(dplyr)
```

# Univariate CoR: Nonparametric Threshold Modeling {#cor-threshold}

An extension of the unadjusted nonparametric threshold-searching approach
developed in @Donovan, the covariate-adjusted TMLE-based approach developed by
van der Laan, Zhang, Gilbert (in progress) is used to estimate the so-called
threshold-response function $E_X[ E[Y|S \geq s, X, A = 1]|A=1]$ for a range of
thresholds $s$. Here, $X$ is a set of baseline characteristics, $A=1$ represents
the vaccine group, $S$ is the biomarker/immune-response/correlate of interest,
and $Y$ is the indicator of COVID disease before some time point $t_f$. This
parameter can be viewed as a causal version of the parameter $P(Y=1|S \geq s,
A=1)$ Intuitively, the threshold-response at a given threshold is the expected
probability of obtaining COVID disease if one experiences a
marker/immune-response value above that threshold. The threshold-response
function is estimated for each of the Day 29 and Day 57 antibody markers, in each case
adjusting for the baseline covariates: age, baseline risk score, high risk
indicator, and underrepresented minority status.A parametric learner, selected
via cross-validation, is used for the covariate adjustment. A number of plots
and tables are reported:
1. A plot and table with risk estimates and point-wise 95% confidence intervals
   for the threshold-response at a grid of thresholds.
2. A plot and table with risk estimates and simultaneous 95% confidence bands
   for the threshold-response at a grid of thresholds.
3. Versions of items 1. and 2. with a monotonicity adjustment.

A histogram of the marker values is superimposed on the threshold-response plots
and a dashed red line is added to mark the threshold value after which no more
events are observed.

\newpage
## Plots and Tables with estimates and pointwise confidence interval for Day 57

\newpage

```{r, include = FALSE}
marker <- "Spike protein binding antibody"
key <- "bindSpike"
day <- 57
ci <- "pointwise"
monotone <- F

```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage 

```{r, include = FALSE}
marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 57
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 57
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 57
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

##  Plots and Tables with estimates and pointwise confidence intervals for Day 29
\newpage

```{r, include = FALSE}
# DAY 29
marker <- "Spike protein antibody"
key <- "bindSpike"
day <- 29
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```

\newpage 

```{r, include = FALSE}

marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 29
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 29
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 29
ci <- "pointwise"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```




\newpage
## Plots and Tables with estimates and pointwise confidence interval for Day 57 (monotone-corrected)

\newpage
```{r, include = FALSE}
marker <- "Spike protein binding antibody"
key <- "bindSpike"
day <- 57
ci <- "pointwise"
monotone <- T

```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage 

```{r, include = FALSE}
marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 57
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 57
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 57
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

##  Plots and Tables with estimates and pointwise confidence intervals for Day 29 (monotone-corrected)

\newpage
```{r, include = FALSE}
# DAY 29
marker <- "Spike protein antibody"
key <- "bindSpike"
day <- 29
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```

\newpage 

```{r, include = FALSE}

marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 29
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 29
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 29
ci <- "pointwise"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```



\newpage
## Plots and Tables with estimates and simultaneous confidence bands for Day 57
\newpage 

```{r, include = FALSE}
marker <- "Spike protein binding antibody"
key <- "bindSpike"
day <- 57
ci <- "simultaneous"
monotone <- F

```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage 

```{r, include = FALSE}
marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 57
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 57
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 57
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

##  Plots and Tables with estimates and simultaneous confidence bands for Day 29

\newpage
```{r, include = FALSE}
# DAY 29
marker <- "Spike protein antibody"
key <- "bindSpike"
day <- 29
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```

\newpage 

```{r, include = FALSE}

marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 29
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 29
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 29
ci <- "simultaneous"
monotone <- F
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```




\newpage
## Plots and Tables with estimates and pointwise confidence interval for Day 57 (monotone-corrected)

\newpage
```{r, include = FALSE}
marker <- "Spike protein binding antibody"
key <- "bindSpike"
day <- 57
ci <- "simultaneous"
monotone <- T

```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage 

```{r, include = FALSE}
marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 57
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 57
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include=FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 57
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

##  Plots and Tables with estimates and pointwise confidence intervals for Day 29 (monotone-corrected) 
\newpage

```{r, include = FALSE}
# DAY 29
marker <- "Spike protein antibody"
key <- "bindSpike"
day <- 29
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```

\newpage 

```{r, include = FALSE}

marker <- "RBD binding antibody"
key <- "bindRBD"
day <- 29
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (50\\% titer)"
key <- "pseudoneutid50"
day <- 29
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}

```

\newpage

```{r, include = FALSE}
marker <- "Pseudo virus-neutralizing antibody (80\\% titer)"
key <- "pseudoneutid80"
day <- 29
ci <- "simultaneous"
monotone <- T
```

```{r, child=here::here('cor_threshold','sub_report.Rmd')}


```