---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, echo = F, include = F}
if(monotone) {
  key0 <- "monotone_"
  add_line <- "The estimates and confidence intervals are adjusted using the assumption that the true threshold-response is nonincreasing."
  add_term <- "monotone-corrected "
} else{
  key0 <- ""
  add_line <- ""
  add_term <- ""
}
if(ci == "simultaneous") {
  ci_key <- "simult"
} else{
  ci_key <- ci
}

ci_label <- paste0(ci, " ")

```

### Day `r day` `r marker`


\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{`r here::here( "figs", paste0(ci,"_CI"), paste0("PLOT_",key0, "Day", day, key, "_", ci_key, "CI.pdf"))`}
\caption{Adjusted threshold-response function for a range of thresholds of the
  Day `r day` `r marker` levels with `r ci` 95\% confidence intervals. The dashed red line marks the threshold after which no more COVID events are observed. `r add_line`}
\end{figure}

```{r, output = "asis", echo = FALSE}
ptwise_tab_guts <- readRDS(here::here( "figs", paste0(ci,"_CI"), paste0("TABLE_", key0, "Day", day, key, "_", ci_key, "CI.rds")))
knitr::kable(ptwise_tab_guts, format = "latex", row.names = F, booktabs = TRUE, escape = FALSE,
            caption = paste0("Table of ", add_term,"risk estimates for a range of thresholds of Day ", day, " ", marker, " levels with ", ci_label,"95\\% confidence intervals."),
              linesep = "") %>%
    kableExtra::kable_styling(latex_options = c("scaled_down", "striped","hold_position") )
```

<!-- \newpage -->

<!-- \begin{figure}[H] -->

<!-- \centering -->
<!-- \includegraphics[width=0.9\textwidth]{`r here::here( "figs", "simultaneous_CI", paste0("PLOT_Day", day, key, "_simultCI.pdf"))`} -->
<!--   \caption{Adjusted threshold-response function for a range of thresholds of the Day `r day` `r marker` activity levels with simultaneous 95\% confidence bands. The dashed red line marks the threshold after which no more COVID events are observed. } -->
<!-- \end{figure} -->

<!-- ```{r, output = "asis", echo = FALSE} -->
<!-- simul_tab_guts <- readRDS(here::here( "figs", "pointwise_CI", paste0("TABLE_Day", day, key, "_pointwiseCI.rds"))) -->
<!-- knitr::kable(simul_tab_guts, format = "latex", row.names = F, booktabs = TRUE, escape = FALSE, -->
<!--              caption = paste0("Table of risk estimates for a range of thresholds of Day ", day, " ", marker, " levels with simultaneous 95\\% confidence intervals."), -->
<!--                linesep = "") %>% -->
<!--     kableExtra::kable_styling(latex_options = c("scaled_down", "striped","hold_position"), ) -->
<!-- ``` -->

<!-- \newpage -->


<!-- \begin{figure}[H] -->

<!-- \centering -->
<!-- \includegraphics[width=0.7\textwidth]{`r here::here( "figs", "pointwise_CI", paste0("PLOT_monotone_Day", day, key, "_pointwiseCI.pdf"))`} -->
<!--   \caption{Assuming nonincreasing monotonicity of the true function, the plot shows the estimated (monotone) adjusted threshold-response function for a range of thresholds of the Day `r day` `r marker` activity levels with point-wise 95\% confidence intervals. The dashed red line marks the threshold after which no more COVID events are observed. } -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

<!-- \centering -->
<!-- \includegraphics[width=0.7\textwidth]{`r here::here( "figs", "simultaneous_CI", paste0("PLOT_monotone_Day", day, key, "_simultCI.pdf"))`} -->
<!--   \caption{Assuming nonincreasing monotonicity of the true function, the plot shows the estimated (monotone) adjusted threshold-response function for a range of thresholds of the Day `r day` `r marker` activity levels with simultaneous 95\% confidence intervals. The dashed red line marks the threshold after which no more COVID events are observed.} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

<!-- \centering -->

<!-- \includegraphics[width=0.8\textwidth]{figs/pointwise_CI/PLOT_INVERSE_Day`r day``r key`_pointwiseCI.pdf} -->

<!--   \caption{The inverse adjusted threshold-response function for thresholds of Day `r day` `r marker` activity levels with pointwise 95\% confidence intervals.} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
<!-- \centering -->
<!-- \includegraphics[width=0.8\textwidth]{figs/pointwise_CI/TABLE_INVERSE_Day`r day``r key`_pointwiseCI.pdf} -->
<!--   \caption{ This analysis assumes monotonicity of the true function. The table displays the estimated threshold of protection of Day `r day` `r marker` activity level at a range of risk levels with pointwise 95\% confidence intervals. } -->

<!-- \end{figure} -->


<!-- \newpage  -->


<!-- \begin{figure}[H] -->

<!-- \centering -->

<!-- \includegraphics[width=0.8\textwidth]{figs/simultaneous_CI/PLOT_INVERSE_Day`r day``r key`_simultCI.pdf} -->

<!--   \caption{This analysis assumes monotonicity of the true function. The plot shows the inverse adjusted threshold-response function for thresholds of Day `r day` `r marker` activity levels with simultaneous 95\% confidence intervals.} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
<!-- \centering -->
<!-- \includegraphics[width=0.8\textwidth]{figs/simultaneous_CI/TABLE_INVERSE_Day`r day``r key`_simultCI.pdf} -->
<!--   \caption{ This analysis assumes monotonicity of the true function. The table displays the estimated threshold of protection of Day `r day` `r marker` activity level at a range of risk levels with simultaneous 95\% confidence bands } -->

<!-- \end{figure} -->
