---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, echo = F, include = F}
if(monotone) {
  key0 <- "monotone_"
  add_line <- "The estimates and confidence intervals are adjusted using the assumption that the true threshold-response is nonincreasing."
  add_term <- "monotone-corrected "
} else{
  key0 <- ""
  add_line <- ""
  add_term <- ""
}
if(ci == "simultaneous") {
  ci_key <- "simult"
} else{
  ci_key <- ci
}

ci_label <- paste0(ci, " ")

```

\newpage

### Day `r day` `r marker`

\begin{figure}[H]
\centering
\includegraphics[width=0.75\textwidth]{`r here::here("cor_threshold", "figs", paste0(ci,"_CI"), paste0("PLOT_",key0, "Day", day, key, "_", ci_key, "CI.pdf"))`}
\caption{Adjusted threshold-response function for a range of thresholds of the
  Day `r day` `r marker` levels with `r ci` 95\% confidence intervals. The dashed red line marks the threshold after which no more COVID events are observed. `r add_line`}
\end{figure}
```{r, output = "asis", echo = FALSE}
ptwise_tab_guts <- readRDS(here::here("cor_threshold",  "figs", paste0(ci,"_CI"), paste0("TABLE_", key0, "Day", day, key, "_", ci_key, "CI.rds")))
knitr::kable(ptwise_tab_guts, format = "latex", row.names = F, booktabs = TRUE, escape = FALSE,
            caption = paste0("Table of ", add_term,"risk estimates for a range of thresholds of Day ", day, " ", marker, " levels with ", ci_label,"95\\% confidence intervals."),
              linesep = "") %>%
    kableExtra::kable_styling(latex_options = c("scaled_down", "striped","hold_position") )
```

\newpage
