---
title: risk score verification code
output: html_document
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
#-----------------------------------------------
# obligatory to append to the top of each script
renv::activate(project = here::here("..", "..", ".."))
source(here::here("..", "..", "..", "_common.R"))
#-----------------------------------------------
library(here)
```
### Data cleaning results

The first twenty rows of the predictor data used by the super learner are shown below.

```{r, show-data, echo = FALSE}
x <- readRDS(here::here("data_clean", "x.rds"))
head(x, 20)
```

After data cleaning, there were `r nrow(x)` observations used in the super learner.

A table of the outcome data are shown below.

```{r, show-outcome-data, echo = FALSE}
y <- readRDS(here::here("data_clean", "y.rds"))
table(y)
```

### Screening results

```{r, set-up-screen, echo = FALSE}
source(here::here("code", "sl_screen_fn.R"))
```

The maximum number of variables adjusted for in the screening functions is `r max_var`.

To double check the output of the screening functions, I will set a seed and run the full data through.

```{r, show-screening-outcomes, echo = TRUE}
screen_all(X = x, Y = y, family = binomial())
# need to set seed for this one
set.seed(123)
screen_glmnet(X = x, Y = y, family = binomial())
screen_univariate_logistic_pval(X = x, Y = y, family = binomial())
screen_highcor_random(X = x, Y = y, family = binomial())
```

### CV-AUC results

Below are the CV-AUC results across the ten repeated cross-validations rounded to four digits. The first column shows the seed that was set prior to running the super learner.

```{r cvauc-tab, echo = FALSE}
cv_auc_tab <- readRDS(here::here("output", "cv_auc_tab.rds"))
seeds <- readRDS(here::here("output", "seeds.rds"))

knitr::kable(data.frame(seed = seeds, cv_auc_tab), digits = 4)
```

The average AUC across the ten runs was `r mean(cv_auc_tab$cvAUC)`.


### Super learner results

Below is the fitted super learner object on the full data.

```{r, show-sl, echo = FALSE}
sl_fit <- readRDS(here("output", "sl_fit.rds"))
sl_fit
```

Below are summary statistics of the risk score.

```{r summary-stat-risk, echo = FALSE}
risk_scores <- readRDS(here("output", "risk_scores.rds"))
summary(risk_scores)
```

Here is a histogram:

```{r hist-risk}
hist(risk_scores)
```

Here are the first 50 risk scores.

```{r show-risks}
head(risk_scores, 50)
```