---
  header-includes:
  - \usepackage{float}
output:
  pdf_document: default
html_document: default
citation_package: natbib
number_sections: true
extra_dependencies: ["caption", "subcaption", "graphicx"]
toc: true
---

# Baseline Risk Score (Proxy for SARS-CoV-2 Exposure) {#baseline-riskscore}

```{r riskVarstable, warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse, quietly = T)
library(kableExtra, quietly = T)
library(conflicted, quietly = T)
conflicted::conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")

caption <- "Variables considered for risk score analysis."

read.csv(here("base_riskscore", "output", "risk_vars.csv"), row.names = 1,
         header = TRUE) %>%
  kable(
    #format = output_type,
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  column_spec(2, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9)
# %>%
# footnote(c("Missing values for variables not dropped from analysis were imputed."),
#          threeparttable = TRUE)
```

\clearpage

```{r learner-screens, warning=FALSE, echo=FALSE}
caption <- "All learner-screen combinations (28 in total) used as input to the superlearner."

read.csv(here::here("base_riskscore", "output", "learner-screens.csv"),
         row.names = 1, header = TRUE) %>%
  rename(`Screen*` = `Screen.`) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  column_spec(1:2, width = "5cm") %>%
  row_spec(0,bold=TRUE) %>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  footnote(c("*Screen details:",
             "all: includes all variables",
             "glmnet: includes variables with non-zero coefficients in the standard implementation of SL.glmnet that optimizes the lasso tuning parameter via cross-validation",
             "univar_logistic_pval: Wald test 2-sided p-value in a logistic regression model < 0.10",
             "highcor_random: if pairs of quantitative variables with Spearman rank correlation > 0.90, select one of the variables at random"),
           threeparttable = TRUE)

```

\clearpage

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{`r here::here("base_riskscore", "figs", "risk_placebo_cvaucs.png")`}
\caption{Risk score analysis with EventIndPrimaryD57 as the outcome: Plot shows CV-AUC point estimates and 95\% confidence intervals for the Super Learner and all models trained to classify cases in placebo group defined by EventIndPrimaryD57. Learners are sorted by their CV-AUC point estimates.}
\label{fig:risk_placebo_cvaucs}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{`r here::here("base_riskscore", "figs", "predProb_riskscore_plac.png")`}
\caption{Plots showing CV estimated probabilities of COVID disease split by cases and controls based off EventIndPrimaryD57 for the top 2 learners, SuperLearner and Discrete SL.}
\label{fig:predProb_riskscore_plac}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{`r here::here("base_riskscore", "figs", "ROCcurve_riskscore_plac.png")`}
\caption{ROC curves for the top 2 learners, SuperLearner and Discrete SL.}
\label{fig:ROCcurve_riskscore_plac}
\end{figure}

\clearpage

```{r risk-sl-weights, warning=FALSE, echo=FALSE}
caption <- "Weights assigned by Superlearner (risk score analysis)."
read.csv(here("base_riskscore", "output", "SL_weights.csv"), row.names = 1,
         header = TRUE) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  row_spec(0,bold=TRUE)
```

\begin{landscape}
\clearpage

```{r SLtopmodels, warning=FALSE, echo=FALSE}
caption <- "Predictors in learners assigned weight > 0.5 by SuperLearner (risk score analysis)."

read.csv(here("base_riskscore", "output", "SL_all_models_with_predictors.csv"),
         row.names = 1, header = TRUE) %>%
  filter(SL.Weights > 0.5) %>%
  mutate(across(.cols = everything(), ~gsub(" ", "", ., fixed = TRUE))) %>%
  mutate(across(.cols = everything(), ~na_if(., "NA"))) %>%
  select_if(~sum(!is.na(.)) > 0) %>%
  kable(
    longtable = T,
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"),
                font_size = 5) %>%
  row_spec(0,bold=TRUE)
```
\end{landscape}
