---
output:
  pdf_document: default
  html_document: default
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,caption,pdflscape,float}
   - \usepackage[margin=1in]{geometry}
---

# Stochastic Interventional Vaccine Efficacy {#cop-stochastic}

```{r cop-stochastic-setup, echo = FALSE, message = FALSE, warning=FALSE}
here::i_am("cop_stochastic/report.Rmd")
renv::activate(project = here::here())
library(here)
library(knitr)
library(stringr)
source(here("_common.R"))
source(here("cop_stochastic", "code", "params.R"))

# make figures bigger
knitr::opts_chunk$set(
  out.width = "95%",
  fig.width = 8,
  results = "asis"
)
```

We estimate the counterfactual mean of symptomatic COVID-19 infection under
posited shifts in the measured activity levels of each of
`r length(marker_to_name)` _candidate_ mechanistic correlates of protection
(mCoP) biomarkers. By shifting the _standardized_ biomarker activity levels by
standard unit shifts along the grid {`r delta_grid`}, we can assess the degree
to which vaccines that modulate mCoP biomarker activity to these levels could
mitigate symptomatic COVID-19 infection in terms of counterfactual stochastic
interventional risk and vaccine efficacy (VE).

## Figures for Stochastic Interventional CoPs for Day 57 {#sve-day57}

```{r cop-stochastic-day57-setup, echo=FALSE, message=FALSE}
# munging marker names
this_time <- "Day57"
this_time_print <- gsub("^(.{3})(.*)$", "\\1 \\2", this_time)
markers_name_short <- str_remove(markers[, this_time], this_time)
```

### Stoch interv. risk: `r marker_to_name[[markers_name_short[1]]]`

```{r marker1-risk-day57, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[1]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[1], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[1]]]`

```{r marker1-sve-day57, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[1]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[1], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[2]]]`

```{r marker2-risk-day57, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[2]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[2], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[2]]]`

```{r marker2-sve-day57, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[2]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[2], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[3]]]`

```{r marker3-risk-day57, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[3]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[3], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[3]]]`

```{r marker3-sve-day57, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[3]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[3], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[4]]]`

```{r marker4-risk-day57, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[4]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[4], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[4]]]`

```{r marker4-sve-day57, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[4]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[4], ".pdf")
  )
)
```

\clearpage

## Figures for Stochastic Interventional CoPs for Day 29 {#sve-day29}

```{r cop-stochastic-day29-setup, echo=FALSE, message=FALSE}
# munging marker names
this_time <- "Day29"
this_time_print <- gsub("^(.{3})(.*)$", "\\1 \\2", this_time)
markers_name_short <- str_remove(markers[, this_time], this_time)
```

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[1]]]`

```{r marker1-risk-day29, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[1]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[1], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[1]]]`

```{r marker1-sve-day29, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[1]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[1], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[2]]]`

```{r marker2-risk-day29, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[2]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[2], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[2]]]`

```{r marker2-sve-day29, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[2]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[2], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[3]]]`

```{r marker3-risk-day29, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[3]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[3], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[3]]]`

```{r marker3-sve-day29, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[3]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[3], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. risk: `r marker_to_name[[markers_name_short[4]]]`

```{r marker4-risk-day29, fig.cap = paste("Stochastic interventional risk estimates, with confidence intervals, for", marker_to_name[[markers_name_short[4]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_risk_", this_time, markers_name_short[4], ".pdf")
  )
)
```

\clearpage

### Stoch. interv. VE: `r marker_to_name[[markers_name_short[4]]]`

```{r marker4-sve-day29, fig.cap = paste("Stochastic interventional VE estimates, with confidence intervals, for", marker_to_name[[markers_name_short[4]]], "at", this_time_print)}
include_graphics(
  here(
    "cop_stochastic", "figs",
    paste0("mcop_sve_", this_time, markers_name_short[4], ".pdf")
  )
)
```
