

```{r varsets, warning=FALSE, echo=FALSE}
caption <- "The 14 variable sets on which an estimated optimal surrogate was built."

read.csv(paste0(here(), "/SL_estimated_optimal_surrogate/output/varsets.csv"), row.names = 1, header = TRUE) %>%
    rename(`Variable Set Name` = `Variable.Set.Name`,
           `Variables included in the set` = `Variables.included.in.the.set`) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  column_spec(2, width = "15cm") %>%
  row_spec(0,bold=TRUE) #%>%
  # footnote(c("If the quantitative fold-rise marker passed the screen, it was included with both a 2-fold and 4-fold rise indicator.",
  #            "The 2-fold and 4-fold rise indicator variables were not part of the variable screening process."),
  #          threeparttable = TRUE)

```




\clearpage

### Endpoint EventIndPrimaryD57, Vaccine group, Phase 2 data

```{r SLperformance-vacc-yd57, warning=FALSE, echo=FALSE}
caption <- "Performance of Superlearner and the top-performing learner-screen combinations (CV-AUCs with 95\\% CIs) for each of the 14 variable sets in the vaccine group with EventIndPrimaryD57 as outcome."

read.csv(paste0(here(), "/SL_estimated_optimal_surrogate/output/SLperformance-vacc-yd57.csv"), row.names = 1, header = TRUE) %>%
    rename(`Variable Set` = `Variable.set`,
           `SL CV-AUC (95% CI)` = `SL.CV.AUC..95..CI.`,
           `CV-AUC (95% CI)` = `CV.AUC..95..CI.`) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 8)  %>%
  footnote(c("*Top-performing Superlearner and individual learner models are highlighted with an asterisk."),
           threeparttable = TRUE)

```


\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{SL_estimated_optimal_surrogate/output/optsurrogate_vacc_cvaucs}
    \caption{Forest Plot showing CV-AUC point estimates and 95\% confidence intervals for the Super Learner and all models in the 2nd variable set trained to classify COVID cases defined by EventIndPrimaryD57 in vaccine group. Learners are sorted by their CV-AUC point estimates.}
    \label{fig:optsurrogate_vacc_cvaucs}
    \end{figure}


\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{SL_estimated_optimal_surrogate/output/predProb_yd57_vacc_2_varset_bAbSpike}
    \caption{Plots showing CV estimated probabilities of COVID disease split by cases and controls based off EventIndPrimaryD57 for the top 2 learners, SuperLearner and Discrete SL in the 2nd variable set of the vaccine group.}
    \label{fig:predProb_yd57_vacc_2_varset_bAbSpike}
    \end{figure}
    
    
\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{SL_estimated_optimal_surrogate/output/ROCcurve_yd57_vacc_2_varset_bAbSpike}
    \caption{ROC curves for the top 2 learners, SuperLearner and Discrete SL in the 2nd variable set of the vaccine group.}
    \label{fig:ROCcurve_yd57_vacc_2_varset_bAbSpike}
    \end{figure}
    


```{r optsurr-sl-weights, warning=FALSE, echo=FALSE}
caption <- "Weights assigned by Superlearner (optimal surrogate analysis)."

read.csv(paste0(here(), "/SL_estimated_optimal_surrogate/output/SL_weights.csv"), row.names = 1, header = TRUE) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  #column_spec(1:2, width = "5cm") %>%
  row_spec(0,bold=TRUE) 

```




```{r optsurr-xgboost-covars, warning=FALSE, echo=FALSE}
caption <- "Predictors in the xgboost model."

read.csv(paste0(here(), "/SL_estimated_optimal_surrogate/output/xgboost_covars.csv"), row.names = 1, header = TRUE) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  #column_spec(1:2, width = "5cm") %>%
  row_spec(0,bold=TRUE) 

```







