---
title: "Verification Report: immuno_tabular"
author: "Yiwen Lu"
date: "2021/04/17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(testthat)
library(here)
```

## Description

This is the verification report for the `immuno_tabular` folder of the `correlates_reporting` project for CoVPN. 

In this document, the output of `make_table_all.R` is compared against the output of `immuno_table_verification.Rmd`. The two scripts use the same base mock data. The two datasets generated by each of the two scripts will be compared with each other to confirm they contain the same values.

`immuno_table_verification.Rmd` was independently double programmed based on the specifications found in `table_specifications.pdf`. This script outputs its processing to \newline 
`verification/verification_output/immuno_tabular_verification_output_tables1.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table2.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table3.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table5.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table6.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table7.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table8.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table9.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table10.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table11.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table12.Rdata`.

The file `verification/verification_input/practice_data.csv` and \newline  `verification/verification_input/Tables_verificatiton_immuno.Rdata` were provided by the original programmer to the tester for verification purposes of `make_table_all.R` when all time points are available.
Their md5 hash are `r digest::digest(file = here("verification/verification_input","practice_data.csv"))`, `r digest::digest(file = here("verification/verification_input","Tables_verificatiton_immuno.Rdata"))`.

The file `verification/verification_output/immuno_tabular_verification_output_tables1.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table2.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table3.Rdata`,\newline  `verification/verification_output/immuno_tabular_verification_output_table5.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table6.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table7.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table8.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table9.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table10.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table11.Rdata`,\newline 
`verification/verification_output/immuno_tabular_verification_output_table12.Rdata` were created by the tester for verification using the `immuno_table_verification.Rmd` script and using all time points available.
Their md5 hash are `r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_tables1.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table2.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table3.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table5.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table6.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table7.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table8.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table9.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table10.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table11.Rdata"))`, \newline 
`r digest::digest(file = here("verification/verification_output/immuno_tabular_verification_output_table12.Rdata"))`.

### Load Data

```{r Load-Data, message=FALSE}
original_data <- load(
  here("verification","verification_input","Tables_verificatiton_immuno.Rdata")
  )
verification_data1 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_tables1.Rdata")
  )
verification_data2<- load(
  here("verification","verification_output","immuno_tabular_verification_output_table2.Rdata")
  )
verification_data3 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table3.Rdata")
  )
verification_data5 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table5.Rdata")
  )
verification_data6 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table6.Rdata")
  )
verification_data7 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table7.Rdata")
  )
verification_data8 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table8.Rdata")
  )
verification_data9<- load(
  here("verification","verification_output","immuno_tabular_verification_output_table9.Rdata")
  )
verification_data10 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table10.Rdata")
  )
verification_data11 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table11.Rdata")
  )
verification_data12 <- load(
  here("verification","verification_output","immuno_tabular_verification_output_table12.Rdata")
  )
```

## Verification

```{r comparison-full}
tab_dm_neg[] <- lapply(tab_dm_neg, as.character)
suppressWarnings(testthat::expect_equal(rr_table1.1, tab_dm_neg))

tab_dm_pos[] <- lapply(tab_dm_pos, as.character)
suppressWarnings(testthat::expect_equal(rr_table1.2, tab_dm_pos))

tab_bind[] <- lapply(tab_bind, as.character)
suppressWarnings(testthat::expect_equal(tab_bind, rr_table2_all))

tab_pseudo[] <- lapply(tab_pseudo, as.character)
suppressWarnings(testthat::expect_equal(tab_pseudo, rr_table3_all_sub))

tab_gm[] <- lapply(tab_gm, as.character)
suppressWarnings(testthat::expect_equal(tab_gm, rr_table5_all))

tab_gmr[] <- lapply(tab_gmr, as.character)
suppressWarnings(testthat::expect_equal(tab_gmr, rr_table6_all))

tab_rgmt[] <- lapply(tab_rgmt, as.character)
suppressWarnings(testthat::expect_equal(tab_rgmt, rr_table7_all))

tab_rrdiff[] <- lapply(tab_rrdiff, as.character)
suppressWarnings(testthat::expect_equal(tab_rrdiff, rr_table8_all))

tab_neg[] <- lapply(tab_neg, as.character)
suppressWarnings(testthat::expect_equal(tab_neg, rr_table9_all))

tab_pos[] <- lapply(tab_pos, as.character)
suppressWarnings(testthat::expect_equal(tab_pos, rr_table10_all))

tab_vacc[] <- lapply(tab_vacc, as.character)
suppressWarnings(testthat::expect_equal(tab_vacc, rr_table11_all))

tab_plcb[] <- lapply(tab_plcb, as.character)
suppressWarnings(testthat::expect_equal(tab_plcb, rr_table12_all))
```


## Signatures

```{r echo = FALSE, message = FALSE, tidy = FALSE, cache = FALSE, results = 'asis'}
suppressWarnings({
suppressPackageStartupMessages({
library(knitr)
library(kableExtra)
library(tibble)
})})
options(kableExtra.latex.load_packages = FALSE, 
        knitr.table.format = "latex",
        knitr.kable.NA = '',
        width = 40,
        usethis.quiet = TRUE)
signature_table <- function(people){
  # check that the tables have correct variables
  if (!all(c("role", "name") %in% tolower(names(people)))) {
    stop(paste0("people table must have variables: role and name. ",
                "Contains: ", paste0(tolower(names(people)), collapse = ", ")))
  }
  
  people$signature <- NA
  people$date <- NA
  names(people) <- tolower(names(people))
  people[, c("role", "name", "signature", "date")] %>% 
  kable(col.names = c("Role", "Name", "Signature", "Date"),
        escape = FALSE, booktabs = FALSE) %>% 
    kable_styling(full_width = FALSE, position = "left") %>% 
    row_spec(0, background = rgb(184, 204, 228, maxColorValue = 255)) %>% 
    column_spec(1, width = "9em", border_left = TRUE) %>% 
    column_spec(2, width = "11em") %>% 
    column_spec(3, width = "15em") %>% 
    column_spec(4, width = "8em", border_right = TRUE)
}
tibble::tribble(
  ~ name,                ~ role,
  "Yiwen Lu",  "Tester"
) %>% 
  signature_table()
```