---
title: "COVID correlates analysis report CoR"
shorttitle: "COVID correlates analysis CoR"
author:
header-includes:
   - \usepackage{float}
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    number_sections: true
    extra_dependencies: ["caption", "subcaption", "graphicx"]
    toc: false
linkcolor: blue
bibliography: ref.bib
---

```{r, include=FALSE}
source(here::here("..", "_common.R"), local = knitr::knit_global())
```
<!-- Note that there is no need to source _common.R in report.Rmd because it is taken care of elsewhere in yml -->


\counterwithin{table}{section}
\counterwithin{figure}{section}


\newif\ifENSEMBLE
`r if (study_name_code=="ENSEMBLE") "\\ENSEMBLEtrue"` 



```{r, echo=FALSE}
Day <- 29
pathCoRoutput <- "output/D29"
```

```{r, child=if (has29) c(here::here('.', 'report_sub.Rmd'))}
```

\clearpage



```{r, echo=FALSE}
Day <- 57
pathCoRoutput <- "output/D57"
```

```{r, child=if (has57) c(here::here('.', 'report_sub.Rmd'))}
```



\clearpage
<!-- The following are not repeated between D29 analyses and D57 analyses -->


\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/barplot_visit_intervals_immuno}
    \caption{Distribution of the number of days bewteen visits in the immunogenicity subcohort, vaccine arm, baseline negative.}
\end{figure}


\ifENSEMBLE
\else

<!-- COVE only -->
\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/barplot_mixed}
    \caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\end{figure}


\fi
