<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->


```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_coxph report ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```


# Graphical Descriptions of Time to Event Data {#cor-graphical-time-to-event}

`r 
tt=timepoints
if (two_marker_timepoints) { 
  paste0("
\\begin{figure}[H]
    \\centering
    \\includegraphics[width=1\\textwidth]{", paste0("cor_coxph/output/", attr(config,"config"), "/D", tt[1], "D", tt[2]), "/barplot_mixed}
    \\caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\\end{figure}
")} else {
  paste0("This page is empty.")
}
`


<!-- these latex variables are used in report_sub -->
\newif\ifCOVE
\newif\ifENSEMBLE
`r paste0("\\", study_name_code, "true")` 



```{r, echo=FALSE, results='asis'}

if(file.exists(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd')))) {
  
  message ("study specific rmd found")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')

} else {

  for (tpeak in tt) {
    COR <- paste0("D", tpeak)
    special.note = ""
    pathCoRoutput <- paste0("cor_coxph/output/", attr(config,"config"), "/", COR)
    res = knitr::knit_child(c(here::here('cor_coxph', 'report_sub.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }

}
```
