<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->

\newif\ifENSEMBLE
`r if (study_name_code=="ENSEMBLE") "\\ENSEMBLEtrue"` 



```{r, echo=FALSE}
Day <- 29
pathCoRoutput <- "cor_coxph/output/D29"
```

```{r, child=if (has29) c(here::here('cor_coxph', 'report_sub.Rmd'))}
```


\clearpage


```{r, echo=FALSE}
Day <- 57
pathCoRoutput <- "cor_coxph/output/D57"
```

```{r, child=if (has57) c(here::here('cor_coxph', 'report_sub.Rmd'))}
```


\clearpage
<!-- The following are not repeated between D29 analyses and D57 analyses -->


\ifENSEMBLE

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{cor_coxph/output/D29/barplot_visit_intervals_immuno}
    \caption{Distribution of the number of days bewteen visits in the immunogenicity subcohort, vaccine arm, baseline negative. }
\end{figure}


\else

<!-- COVE only -->

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/barplot_visit_intervals_immuno}
    \caption{Distribution of the number of days bewteen visits in the immunogenicity subcohort, vaccine arm, baseline negative.  The median (IQR) number of days between Day 29 and Day 57 was \protect\input{`r pathCoRoutput`/quartiles_visit_intervals_immuno}.}
\end{figure}


\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/barplot_mixed}
    \caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\end{figure}


\fi