# Day `r COR` Univariate CoR: Cox Models of Risk {#cor-coxph-Day`r COR`}

The main regression model is the Cox proportional hazards model. All plots are made with Cox models fit unless specified otherwise.

## Hazard ratios

\begin{table}[H]
\caption{Inference for Day `r tpeak` antibody marker covariate-adjusted correlates of risk of `r txt.endpoint` in the vaccine group: Hazard ratios per 10-fold increment in the marker*}
\begin{center}
    \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_`r study_name`}\\
\end{center}
*Baseline covariates adjusted for: `r covariates_adjusted`. Maximum failure event time \input{`r pathCoRoutput`/timepoints_cum_risk_`r study_name`} days.\\
**`r txt.coxph.note2`\\
***q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r study_name`} replicates). \\
`r special.note`
    %\label{tab:CoR_univariable_svycoxph_pretty_`r study_name`}
\end{table}


\begin{table}[H]
\caption{Inference for Day `r tpeak` antibody marker covariate-adjusted correlates of risk of `r txt.endpoint` in the vaccine group: Hazard ratios for Middle vs. Upper tertile vs. Lower tertile*}
\begin{center}
\setlength{\tabcolsep}{.5ex}
\input{`r pathCoRoutput`/CoR_univariable_svycoxph_cat_pretty_`r study_name`}\\
\end{center}
*Baseline covariates adjusted for: `r covariates_adjusted`. Maximum failure event time \input{`r pathCoRoutput`/timepoints_cum_risk_`r study_name`} days. Cutpoints:
%Day `r tpeak` cutpoints:
\input{`r pathCoRoutput`/cutpoints_Day`r tpeak`bindSpike_`r study_name`},  
\input{`r pathCoRoutput`/cutpoints_Day`r tpeak`bindRBD_`r study_name`},  
`r if(study_name_code!="ENSEMBLE") paste0("\\input{", pathCoRoutput, "/cutpoints_Day", tpeak, "pseudoneutid50_", study_name, "},")`
`r if(study_name_code!="ENSEMBLE") paste0("\\input{", pathCoRoutput, "/cutpoints_Day", tpeak, "pseudoneutid80_", study_name, "},")`
all on the log10 scale.
\\
**`r txt.coxph.note2`\\
***Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.\\
$\dagger$ q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers `r ifelse(study_name_code=="COVE", "", "")` using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r study_name`} replicates). \\
`r special.note`

    %\label{tab:CoR_univariable_svycoxph_cat_pretty_`r study_name`}
\end{table}

\clearpage


<!-- Forest plots -->

```{r, echo=FALSE, results='asis'}

if(file.exists(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd')))) {
  message ("forest plots")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')
}
```


## Marginalized risk and controlled vaccine efficacy plots


\begin{table}[H] 
\caption{Analysis of Day `r tpeak` markers (upper vs. lower tertile) as a CoR and a controlled risk CoP.}
\begin{center}
\begin{tabular}{lcccccc} \hline 
 & \multicolumn{2}{c}{marginalized risk} & \multicolumn{2}{c}{controlled risk} & & \\ 
 & \multicolumn{2}{c}{ratio $RR_M(0,1)$} & \multicolumn{2}{c}{ratio $RR_C(0,1)^1$} & \multicolumn{2}{c}{e(0,1)$^2$} \\ 
  & Point Est. & 95\% CI  &    Point Est. & 95\% CI  &   Point Est.  & 95\% CI UL \\ \hline
\input{`r pathCoRoutput`/marginalized_risks_cat_`r study_name`}  \\ \hline 
\end{tabular}
\end{center}
$^1$Conservative (upper bound) estimate assuming unmeasured confounding at level $RR_{UD}(0,1)=RR_{EU}(0,1) = 2$ and thus $B(0,1)=4/3$. \\
$^2$E-values are computed for upper tertile ($s=1$) vs. lower tertile ($s=0$) biomarker subgroups after controlling for `r covariates_adjusted`; UL = upper limit.\\
`r special.note`
\end{table}

\clearpage


```{r, echo=FALSE, results='asis'}
  for (a in assays) {
    res = knitr::knit_child(c(here::here('cor_coxph', 'risk_plots.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
  }
```


```{r, echo=FALSE, results='asis'}
  if (!is.null(config$primary_assays)) {
    res = knitr::knit_child(c(here::here('cor_coxph', 'multiple_regression.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
  }
```



