<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->


```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_coxph report ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```


```{r, echo=FALSE, results='asis'}
config.cor <- config::get(config = COR)
```

# Graphical Descriptions of Time to Event Data {#cor-graphical-time-to-event}

`r if (config.cor$two_marker_timepoints) { 
  tt=config.cor$timepoints
  paste0("
\\begin{figure}[H]
    \\centering
    \\includegraphics[width=1\\textwidth]{", paste0("cor_coxph/output/", attr(config,"config"), "/D", tt[1], "D", tt[2]), "/barplot_mixed}
    \\caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\\end{figure}
")} else {
  paste0("This page is empty.")
}
`


<!-- these latex variables are used in report_sub -->
\newif\ifCOVE
\newif\ifENSEMBLE
`r paste0("\\", study_name_code, "true")` 



<!-- handle cove and ensemble differently because they include different analyses -->

<!-- COVE -->

```{r, echo=FALSE, results='asis'}
if (study_name=="COVE" | study_name=="MockCOVE") {
  for (i in 1:2) {
    tpeak <- tt[i]
    COR <- paste0("D", tpeak)
    special.note = ""
    pathCoRoutput <- paste0("cor_coxph/output/", attr(config,"config"), "/", COR)
    res = knitr::knit_child(c(here::here('cor_coxph', 'report_sub.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
```


<!-- D29start1 is ENSEMBLE specific -->

```{r, echo=FALSE, results='asis'}
if (study_name=="MockENSEMBLE" | study_name=="ENSEMBLE") {
  for (i in 1:2) {
    tpeak <- tt[1]
    COR <- ifelse(i==1, "D29", "D29start1")
    special.note = paste0("$\\ddagger$ Count cases starting ", ifelse(i==1,7,1), " days post Day 29.")
    pathCoRoutput <- paste0("cor_coxph/output/", attr(config,"config"), "/", COR)
    res = knitr::knit_child(c(here::here('cor_coxph', 'report_sub.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
```
